Racial and Ethnic Differences in ETI: Outcomes

### 2024-05-10 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
trying to speed up mcp

```{r setup}
#| include: false
# Libraries
library(nlme)
library(performance)
library(segmented)
library(tidyverse)
library(mcp)
options(mc.cores = 4)
set.seed(1017)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| cache: true
model <- list(
  gli_fev1_ppred_rn ~ 1, # intercept
  gli_fev1_ppred_rn ~ 1 ~ 0 + Days # joined slope
)
fit <- mcp(model, data = cleaned)
```

@@

```{r}
#| cache: true
# Fit lme
mod1 <- lme(gli_fev1_ppred_rn ~ Days * Race + Insurance,
  random = ~ 1 | eDWID,
  data = cleaned, na.action = na.omit
)
mod1_seg <- segmented.lme(mod1, ~Days,
  psi = 0,
  random = list(eDWID = pdDiag(~ 1 + Days + U)) # ind. random eff. (changepoint fixed)
)
# mod1_seg <- segmented.lme(mod1, ~Days,
#   psi = 0,
#   random = list(eDWID = pdDiag(~ 1 + Days + U + G0))  #ind. random eff. (in the changepoint too)
# )
```

>>>>

```{r setup}
#| include: false
# Libraries
library(nlme)
library(performance)
library(segmented)
library(tidyverse)
library(mcp)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| cache: true
set.seed(1017)
model <- list(
  gli_fev1_ppred_rn ~ 1, # intercept
  gli_fev1_ppred_rn ~ 1 ~ 0 + Days # joined slope
)
fit <- mcp(model, data = cleaned, chains = 4, cores = 4, iter = 1000, adapt = 0) # Increase iter and adapt later, because it will take forever to run
```

@@

```{r}
#| cache: true
# Fit lme
mod1 <- lme(gli_fev1_ppred_rn ~ Days * Race + Insurance,
  random = ~ 1 | eDWID,
  data = cleaned, na.action = na.omit
)
# mod1_seg <- segmented.lme(mod1, ~Days,
#   psi = 0,
#   random = list(eDWID = pdDiag(~ 1 + Days + U)), # ind. random eff. (changepoint fixed)
#   control = seg.control(n.boot = 0, display = TRUE)
# )
mod1_seg <- segmented.lme(mod1, ~Days,
  psi = 0,
  random = list(eDWID = pdDiag(~ 1 + Days + U + G0)), # ind. random eff. (in the changepoint too)
  control = seg.control(n.boot = 0, display = TRUE)
)
```

```{r}
```
